---
title: "Math Assignment"
subtitle: "ECON 3535: Natural Resource Economics"
author: "Kyle Butts"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  xaringan::moon_reader:
    css: ['default']
    ## No title slide
    seal: false
    self_contained: true
    nature:
      ratio: '8.5:11'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r preamble, child=here::here("document-preamble.Rmd")}
```

```{r, echo = F}
library(icons)
library(tidyverse)
library(gt)
```

<h1 class="hi text-2xl center coral">Practice Math Assignment</h1>

## Two period model of a non-renewable resource

Consider extraction of a non-renewable natural resource. The inverse demand function
for the depletable resource is \\(P = 12 – Q\\) in both periods \\(1\\) and \\(2\\) and the marginal cost of supplying it is \\(\\$3\\). The discount rate is \\(10\\%\\). There are \\(7.5\\) units total.

<ol>
<li>Find the equilibrium allocation in each period for resource extraction</li>

<li>Describe why \(Q_1 = 3\) and \(Q_2 = 4.5\) is not optimal</li>

<li>What is the marginal user cost? Interpret this number.</li>

<li>Now assume \(r = 0\). What is the optimal allocation now? Why did it change in the direction that it did?</li>
</ol>


---

## Two period model of a non-renewable resource

Consider extraction of a non-renewable natural resource. The inverse demand function
for the depletable resource is \\(P = 12 – Q\\) in both periods \\(1\\) and \\(2\\) and the marginal cost of
supplying it is \\(2 + Q/2\\). The discount rate is \\(6\\% \\). There are \\(15\\$\\) units total.

<ol>
<li>Find the equilibrium allocation in each period for resource extraction</li>

<li>What is the marginal user cost? Interpret this number.</li>
</ol>




---

## Tradable Permits

wo firms can control emissions at the following marginal costs: \\(MC_1 = 200 a_x\\) and
\\(MC_2 = 100 a_y\\) where \\(a_x\\) and \\(a_y\\) are, respectively, the amount of emissions reduced by the
first and second firms. Assume that with no control at all, each firm would be emitting \\(20\\)
units of emissions or a total of \\(40\\) units for both firms.

<ol>
<li>Consider a cap-and-trade system that aims for a total reduction of \(21\) units of emis-
sions is necessary. 
  <ul>
  <li>What is the equilibrium allocation of permits to each firm?</li>
  <li>At what price would these permits sell for at an auction</li>
  </ul>
</li>

<li>Assume that the control authority wanted to reach its objective by using an emissions
charge system instead.
  <ul>
  <li>What tax amount should them impose to reach this equilibrium?</li>
  <li>How much revenue would the government collect?</li>
  </ul>
</li>

<li>Why is cap-and-trade more cost-effective than a uniform standard where each firm
reduces pollution by \(10.5\) units?</li>
</ol>


---

## Tradable Permits


Two firms can control emissions at the following marginal costs: \\( MC_1 = 5 + 10 a_x \\) and
\\(MC_2 = 11 a_y\\) where \\(a_x\\) and \\(a_y\\) are, respectively, the amount of emissions reduced by the
first and second firms. Assume that with no control at all, each firm would be emitting \\(20\\)
units of emissions or a total of \\(10\\) units for both firms.

<ol>
<li>Consider a cap-and-trade system that aims for a total reduction of \(21\) units of emis-
sions is necessary. 
  <ul>
    <li>What is the equilibrium allocation of permits to each firm?</li>
    <li>At what price would these permits sell for at an auction</li>
  </ul>
</li>

<li>Assume that the control authority wanted to reach its objective by using an emissions
charge system instead.
  <ul>
    <li>What tax amount should them impose to reach this equilibrium?</li>
    <li>How much revenue would the government collect?</li>
  </ul>
</li>
</ol>

