---
title: "Outline"
subtitle: "ECON 3535: Natural Resource Economics"
author: "Kyle Butts"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  xaringan::moon_reader:
    css: ['default']
    ## No title slide
    seal: false
    self_contained: true
    nature:
      ratio: '8.5:11'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r preamble, child=here::here("document-preamble.Rmd")}
```

```{r, echo = F}
library(icons)
library(tidyverse)
library(gt)
```

<h1 class="hi text-2xl center coral">ECON 3535: Course Outline</h1>

## Unit 1: Economic Fundamentals 
<div style="height: 0.25rem;"></div>

### Lecture 1


- Intro to Class

- Prisoner's Dilemma Review

*Readings for this lecture*

- [Robert Frank's The Darwin Economy](https://kylebutts.com/ECON3535_S2021/Articles/Excerpts%20from%20The%20Darwin%20Economy.pdf)


### Lecture 2


- Economic tools for analyzing natural resource problems

- Discounting and Present Value

*Readings for this lecture*

- "Static Efficiency", page 21

- "Relating Optimality to Efficiency", page 48

- "Comparing Benefits and Costs Across Time", page 49

- "Choosing the Discount Rate", page 60


### Lecture 3


- Resource taxonomy

- Recyclable resources

- Two-period model with constant MC and fixed supply

*Readings for this lecture*

- "Resource Taxonomy", page 124

- "A Two-Period Model", page 108

- [Michael Greenstone's Managing Climate Risk](https://kylebutts.com/ECON3535_S2021/Articles/What%20Financial%20Markets%20Can%20Teach%20Us%20About%20Managing%20Climate%20Risks.pdf) ([online version](https://www.nytimes.com/2017/04/04/upshot/what-financial-markets-can-teach-us-about-managing-climate-risks.html)).


### Lecture 4


- Mineral two-period model

- Marginal user cost

*Readings for this lecture*

- "A Two-Period Model", page 108


---

### Lecture 5


- Two-period model wrap up

- Markets

*Readings for this lecture*

- "Efficient Intertemporal Allocations", page 127


### Lecture 6
  

- Efficiency

- Welfare theorem

- Property rights

*Readings for this lecture*

- "Externalities as a Source of Market Failure", page 25

- Example 2.2 Shrimp Farming Externalities in Thailand, page 27


### Lecture 7


- Coase theorem

- Bargaining

*Readings for this lecture*

- "Externalities as a Source of Market Failure", page 25

- Example 2.2 Shrimp Farming Externalities in Thailand, page 27

- "Coase Theorem", page 36



### Lecture 8


- Policy tools

- Local pollutants

*Readings for this lecture*

- [Ronald Coase and the Misuse of Economics](https://kylebutts.com/ECON3535_S2021/Articles/Ronald%20Coase%20and%20the%20Misuse%20of%20Economics.pdf) ([online version](https://www.newyorker.com/news/john-cassidy/ronald-coase-and-the-misuse-of-economics)).

- "The Command-and-Control Policy Framework", page 358

---

### Lecture 9

- Policy comparisons

- Numerical example

*Readings for this lecture*

- "Command and control vs market-based policies", page 358


### Lecture 10

- Policies Continued

- Numerical Exercise


### Lecture 11

- Taxes and Deadweight Loss

- Corrective Taxes and Subsidies

*Videos*

- [Taxes and Deadweight Loss](https://www.youtube.com/watch?v=NuLlNAdrom4)

- [Pigouvian Taxes](https://www.youtube.com/watch?v=UYShebe44Xs)


### Lecture 12

- Growth and Development

- Trade 

*Readings for this lecture*

- "Trade and the Environment", page 480

- Example 20.3 The Natural Resource Curse

- [Carbon Taxes Won't Do Enough to Slow Global Warming](https://kylebutts.com/ECON3535_S2021/Articles/Carbon%20Taxes%20Wont%20Do%20Enough%20to%20Slow%20Global%20Warming.pdf) ([online version](https://www.bloombergquint.com/business/2019/09/25/carbon-taxes-won-t-do-enough-to-slow-global-warming)).


## Math Assignment due 2/11 at 11:59pm 


---
## Unit 2: Energy Resources
<div style="height: 0.25rem;"></div>

### Lecture 13

- Energy Overview


### Lecture 14

- Electricity Industry

*Readings for this lecture*

- ["Will we ever stop using fossil fuels?"](aeaweb.org/articles?id=10.1257/jep.30.1.117), pages 117-120

- "Electricity" and Examples 7.5 and 7.6, pages 158


### Lecture 15
  
- Coal
  
- Carbon capture and storage
  
- Nuclear

*Readings for this lecture*


### Lecture 16  

- Natural Gas

*Readings for this lecture*

- [Renewable energy - the global transition, explained in 12 charts](https://kylebutts.com/ECON3535_S2021/Articles/Renewable%20energy%20-%20the%20global%20transition,%20explained%20in%2012%20charts.pdf) ([online version](https://www.vox.com/energy-and-environment/2019/6/18/18681591/renewable-energy-china-solar-pv-jobs))


### Lecture 17

- Renewables overview

- Wind
  
*Readings for this lecture*

- [Renewables to Account for a Third of Global Power Generation in 2022](https://kylebutts.com/ECON3535_S2021/Articles/Renewables%20to%20Account%20for%20a%20Third%20of%20Global%20Power%20Generation%20in%202022%20|%20Greentech%20Media.pdf)
([online version](https://www.greentechmedia.com/articles/read/iea-report-renewables-third-global-generation)).

- [Renewables Are Expanding at an Astounding Pace. But It’s Still Not Enough to Meet Climate Goals](https://kylebutts.com/ECON3535_S2021/Articles/Renewables%20Are%20Expanding%20at%20an%20Astounding%20Pace.%20But%20Its%20Still%20Not%20Enough%20to%20Meet%20Climate%20Goals%20|%20Greentech%20Media.pdf)
([online version](https://www.greentechmedia.com/articles/read/renewable-energy-growth-is-still-not-enough-to-meet-climate-goals)).


---
### Lecture 18

- Solar

*Readings for this lecture*

- Interview with NREL Researcher: [Solar power’s greatest challenge was discovered 10 years ago. It looks like a duck. ](https://kylebutts.com/ECON3535_S2021/Articles/Solar%20powers%20greatest%20challenge%20was%20discovered%2010%20years%20ago.%20It%20looks%20like%20a%20duck%20-%20Vox.pdf) ([online version](https://www.vox.com/energy-and-environment/2018/3/20/17128478/solar-duck-curve-nrel-researcher)).


### Lecture 19

- Energy storage

- Demand response

*Readings for this lecture*

- [Energy Storage](http://energystorage.org/energy-storage/faq)

- [Demand Response](https://energy.gov/oe/activities/technology-development/grid-modernization-and-smart-grid/demand-response)


### Lecture 20

- Hydroelectric

- Biofuels

*Videos*

- [The Future of Energy Storage Beyond Lithium Ion](https://www.youtube.com/watch?v=EoTVtB-cSps)


### Lecture 21

- Transportation

*Readings for this lecture*

- "CAFE Standards" and "Alternative Fuels and Vehicles", page 380 and 385


---
## Unit 3: Pollution, Climate Change, and Policy
<div style="height: 0.25rem;"></div>

### Lecture 22 

- Climate change

- Science overview

- Policy overview

*Readings for this lecture*

- [The Uninhabitable Earth](https://kylebutts.com/ECON3535_S2021/Articles/The%20Uninhabitable%20Earth.pdf) ([online version](https://nymag.com/intelligencer/2017/07/climate-change-earth-too-hot-for-humans.html)).


### Lecture 23

- Policies for local air pollution

- US Acid Rain Program

- Programs in France, Sweden, Japan

*Readings for this lecture*

- [NYTimes' The Daily: Joe Biden's Climate Plan](https://www.nytimes.com/2021/02/02/podcasts/the-daily/biden-climate-agenda.html)


### Lecture 24

- International air pollution policies

*Videos*

- [A Brief History of Environmental Justice](https://www.youtube.com/watch?v=30xLg2HHg8Q)

- Example: Cancer Alley [Why This Town is Dying From Cancer](https://www.youtube.com/watch?v=ZB8CbDG7gpk)


### Lecture 25

- Paris Agreement

- Country-specific climate change policies

*Readings for this lecture*

- [Most countries aren't hitting 2030 climate goals, and everyone will pay the price](https://kylebutts.com/ECON3535_S2021/Articles/Most%20countries%20arent%20hitting%202030%20climate%20goals,%20and%20everyone%20will%20pay%20the%20price.pdf) ([online version](https://www.nationalgeographic.com/science/2019/11/nations-miss-paris-targets-climate-driven-weather-events-cost-billions/)).

- [China’s Pledge to Be Carbon Neutral by 2060 - What It Means](https://kylebutts.com/ECON3535_S2021/Articles/Chinas%20Pledge%20to%20Be%20Carbon%20Neutral%20by%202060-%20What%20It%20Means%20-%20The%20New%20York%20Times.pdf) ([online version](https://www.nytimes.com/2020/09/23/world/asia/china-climate-change.html)).

- [John Kerry, Biden’s Climate Czar, Talks About Saving the Planet](https://kylebutts.com/ECON3535_S2021/Articles/John%20Kerry,%20Bidens%20Climate%20Czar,%20Talks%20About%20Saving%20the%20Planet%20—%20ProPublica.pdf) ([online version](https://www.propublica.org/article/john-kerry-biden-climate-czar)).


---
### Lecture 26

- Environmental taxes

- Double dividend hypothesis

*Readings for this lecture*

- [The Trump Administration Is Reversing More Than 100 Environmental Rules. Here’s the Full List.](https://kylebutts.com/ECON3535_S2021/Articles/The%20Trump%20Administration%20Is%20Reversing%20More%20Than%20100%20Environmental%20Rules.%20Here’s%20the%20Full%20List.%20-%20The%20New%20York%20Times.pdf) ([online version](https://www.nytimes.com/interactive/2020/climate/trump-environment-rollbacks-list.html)).

- TBD: about Biden's Climate Efforts 



---
## Unit 4: Valuation Methods and Non-Energy Resources
<div style="height: 0.25rem;"></div>


### Lecture 27

- Valuation overview

- Cost/benefit analysis

- Efficiency

*Readings for this lecture*

- Chapter 3


### Lecture 28

- Different types of value

- Stated preference methods and biases

*Readings for this lecture*

- Chapter 4


### Lecture 29

- Revealed preference methods

*Readings for this lecture*

- Chapter 4


### Lecture 30

- Ecosystem services

*Readings for this lecture*

- Chapter 4


### Lecture 31

- Bioeconomic systems

- Static fisheries

*Readings for this lecture*

- Video: [The economic, social and icon value of the Great Barrier Reef](https://www.youtube.com/watch?v=b3iJ2X9Vjnw)

- [What Is The Real Value Of The Great Barrier Reef?](https://kylebutts.com/ECON3535_S2021/Articles/What%20Is%20The%20Real%20Value%20Of%20The%20Great%20Barrier%20Reef%20|%20HuffPost) ([online version](https://www.huffpost.com/entry/what-is-the-real-value-of-the-great-barrier-reef_b_595cbea4e4b0326c0a8d13c7))

- [What bees can teach us about the real value of protecting nature](https://kylebutts.com/ECON3535_S2021/Articles/What%20bees%20can%20teach%20us%20about%20the%20real%20value%20of%20protecting%20nature%20-%20Vox.pdf) ([online version](https://www.vox.com/2015/7/6/8900605/bees-pollination-ecosystem-services)).

---

### Lecture 32

- Dynamic fisheries

- Open access fisheries

*Readings for this lecture*

- First half of chapter 12 (Until you get to the dynamic fisheries model)


### Lecture 33

- Forestry

*Readings for this lecture*

- Chapter 11

## Writing Assignment due 4/15 at 11:59pm 
<div style="height: 0.25rem;"></div>

### Lecture 34

- Land use

- Food insecurity

*Readings for this lecture*

- Chapter 10


### Lecture 35

- Water

*Readings for this lecture*

- Chapter 9


### Lecture 36

- Waste and Recycling

*Readings for this lecture*

- [Is Recycling Worth It?](https://kylebutts.com/ECON3535_S2021/Articles/Is%20Recycling%20Worth%20It%20-%20Scientific%20American.pdf) ([online version](https://www.scientificamerican.com/article/is-recycling-worth-it/)).


